Well-quasi-orderings on word languages

### 2025-10-10 src/infixes.tex
lemma 8 polishing

\begin{lemma}
    \label{thue-morse-ordinal:lemma}
    The \kl{maximal order type} of $\LMorse$ is $\omegaOrd$,
    the \kl{ordinal height} of $\LMorse$ is $\omegaOrd$,
    the \kl{ordinal width} of $\LMorse$ is $\omegaOrd$.
\end{lemma}
\begin{proof}
    Let us prove that these are upper bounds for the \kl{ordinal invariants} of
    $L$. For the \kl{ordinal height}, it is true for any language $\LMorse$.
    For the \kl{maximal order type}, we remark that
    the maximal length of a \kl{bad sequence} is determined by its first element,
    hence that it is at most $\omegaOrd$.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order type},
    we conclude that the \kl{ordinal width} is also at most $\omegaOrd$.

    Now, let us prove that these bounds are tight. It is clear that
    $\oHeight{\LMorse} = \omegaOrd$: given any number $n \in \Nat$, one can construct a
    \kl{decreasing sequence} of words in $L$ of length $n$, for instance by
    considering the first $n$ prefixes of the \kl{Thue-Morse sequence} by
    decreasing size.
    Let us now prove that $\oWidth{\LMorse} = \omegaOrd$. Assume by contradiction that
    $\oWidth{\LMorse}$ is finite. Then, $L$ can be written as a finite union of
    \kl{chains} for the \kl{infix relation}, and in particular, $L$ is
    \kl(language){bounded}, which is absurd by \cref{thue-morse:lemma}.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order
    type}, we conclude that the \kl{maximal order type} of $\LMorse$ is also $\omegaOrd$.
\end{proof}

>>>>

\begin{lemma}
    \label{thue-morse-ordinal:lemma}
    Under $\infleq$,
    the \kl{maximal order type} of $\LMorse$ is $\omegaOrd$,
    the \kl{ordinal height} of $\LMorse$ is $\omegaOrd$,
    the \kl{ordinal width} of $\LMorse$ is $\omegaOrd$.
\end{lemma}
\begin{proof}
	We first show that $\omegaOrd$ is an upper bound for each of these measure, 
	before showing that the bounds are tight.

    %Let us prove that these are upper bounds for the \kl{ordinal invariants} of
    $\LMorse$. 
    The bound of the \kl{ordinal height} holds for any language $L$,
    since a descending chain for $(\Sigma^*, \infleq)$ is isomorphic to one for $(\Nat, \leq)$ \todo{please check this is a good argument}.
    For the \kl{maximal order type}, we remark that
    the \kl{uniform recurrence} of $\ThueMorse$ means that
    the maximal length of a \kl{bad sequence} is determined by its first element,
    hence that it is at most $\omegaOrd$.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order type} \todo{add reference},
    we conclude that the \kl{ordinal width} is also at most $\omegaOrd$.

    Now, let us prove that these bounds are tight. It is clear that
    $\oHeight{\LMorse} = \omegaOrd$: given any number $n \in \Nat$, one can construct a
    \kl{decreasing sequence} of words in $\LMorse$ of length $n$, for instance by
    considering the first $n$ prefixes of the \kl{Thue-Morse sequence} by
    decreasing size.
    Let us now prove that $\oWidth{\LMorse} = \omegaOrd$. Assume by contradiction that
    $\oWidth{\LMorse}$ is finite. Then, $\LMorse$ can be written as a finite union of
    \kl{chains} for the \kl{infix relation}, and in particular, $\LMorse$ is
    \kl(language){bounded}, which is absurd by \cref{thue-morse:lemma}.
    Finally, because the \kl{ordinal width} is at most the \kl{maximal order
    type}, we conclude that the \kl{maximal order type} of $\LMorse$ is also $\omegaOrd$.
\end{proof}
